Check links on old pages

### 2023-02-24 src/check-old-pages.Rmd
Moved copyright to 00 folder

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2022-02-20"
output: html_document
---

@@

path <- "c:/Users/Steve/Dropbox/professional/fun stuff/update-website"
path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website"
```

>>>>

---
title: "Check links on old pages"
author: "Steve Simon"
date: "Created 2023-02-20"
output: html_document
---

@@

# path <- "c:/Users/Steve/Dropbox/professional/fun stuff/update-website"
path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website"
```
